Emulation of high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2022-10-05 qcd.tex
wrote: antenna expressions (A)

    Antenna functions are constructed from a ratio of
    colour-ordered matrix elements.
    For the case of one unresolved parton, the three-parton
    tree-level antenna function is given by
    \begin{equation}\label{eqn:X30}
        X_{3}^{0}(i, j, k) = S_{ijk,IK} \dfrac{|M_{n+1}^{(0)}(i,j,k)|^{2}}{|M_{n}^{(0)}(I,K)|^{2}}
    \end{equation}
    where $|M_{n}^{(\ell)}|^{2}$ is the $n$-body colour-ordered matrix
    element at loop-level $\ell$. $S_{ijk,IK}$ is a symmetry factor
    accounting for identical particles in the final-state
    and for the presence of multiple antennae in the two-
    parton process. $I$ and $K$ are hard partons forming a colour
    connected antenna that radiates particle $j$. The identities
    of $i/I$ and $k/K$ defines the specific class of the
    antenna function. There are three classes corresponding
    to the three underlying two-parton processes: quark-antiquark,
    quark-gluon and gluon-gluon. Therefore, there will
    be an antenna for every radiative correction to these
    two-parton processes. The physical matrix elements used
    to the derive the antenna functions for each class are as follows:
    \begin{itemize}
        \item Quark-antiquark: $\gamma^{*} \rightarrow q\bar{q}$ + (partons),
        the decay of a virtual photon into a quark-antiquark pair with QCD radiation from the quark pair \cite{Gehrmann-DeRidder:2004ttg}.
        \item Quark-gluon: $\tilde{\chi} \rightarrow \tilde{g}g$ + (partons),
        the decay of a heavy neutralino into a gluino and gluon with QCD radiation from the gluon-gluino pair \cite{Gehrmann-DeRidder:2005svg}.
        \item Gluon-gluon: $H \rightarrow gg$ + (partons),
        the decay of a Higgs boson into a pair of gluons with QCD from the gluon pair \cite{Gehrmann-DeRidder:2005alt}.
    \end{itemize}
    Along with the tree-level antenna, there are also the
    one-loop antennae. For the three-parton case these are given by
    \begin{equation}\label{eqn:X31}
        X_{3}^{1}(i,j,k) = S_{ijk,IK} \dfrac{|M_{n+1}^{(1)}(i,j,k)|^{2}}{|M_{n}^{(0)}(I,K)|^{2}} - X_{3}^{0}(i,j,k) \dfrac{|M_{n}^{(1)}(I,K)|^{2}}{|M_{n}^{(0)}(I,K)|^{2}} \, ,
    \end{equation}
    where $X_{3}^{1}$ are defined such that they are proportional
    to the one-loop singular functions. Since the one-loop
    factorisation formulae (\ref{eqn:1L_soft_factorisation})
    and (\ref{eqn:1L_collinear_factorisation}) are of the form
    $|M^{(1)}_{n+1}|^{2}\rightarrow S^{(0)}|M^{(1)}_{n}|^{2} + S^{(1)}|M^{(0)}_{n}|^{2}$,
    the term proportional to $X_{3}^{0}$ has to be removed
    to fulfill this requirement.
    The antenna functions are summarised in Table~\ref{table:antenna_functions}, where
    antenna functions are categorised by their class and radiative
    processes. A pictorial representation is also given in Figure ...

@@

>>>>

    Antenna functions are constructed from a ratio of
    colour-ordered matrix elements.
    For the case of one unresolved parton, the three-parton
    tree-level antenna function is given by
    \begin{equation}\label{eqn:X30}
        X_{3}^{0}(i, j, k) = S_{ijk,IK} \dfrac{|M_{n+1}^{(0)}(i,j,k)|^{2}}{|M_{n}^{(0)}(I,K)|^{2}}
    \end{equation}
    where $|M_{n}^{(\ell)}|^{2}$ is the $n$-body colour-ordered matrix
    element at loop-level $\ell$. $S_{ijk,IK}$ is a symmetry factor
    accounting for identical particles in the final-state
    and for the presence of multiple antennae in the two-
    parton process. $I$ and $K$ are hard partons forming a colour
    connected antenna that radiates particle $j$. The identities
    of $i/I$ and $k/K$ defines the specific class of the
    antenna function. There are three classes corresponding
    to the three underlying two-parton processes: quark-antiquark,
    quark-gluon and gluon-gluon. Therefore, there will
    be an antenna for every radiative correction to these
    two-parton processes. The physical matrix elements used
    to the derive the antenna functions for each class are as follows:
    \begin{itemize}
        \item Quark-antiquark: $\gamma^{*} \rightarrow q\bar{q}$ + (partons),
        the decay of a virtual photon into a quark-antiquark pair with QCD radiation from the quark pair \cite{Gehrmann-DeRidder:2004ttg}.
        \item Quark-gluon: $\tilde{\chi} \rightarrow \tilde{g}g$ + (partons),
        the decay of a heavy neutralino into a gluino and gluon with QCD radiation from the gluon-gluino pair \cite{Gehrmann-DeRidder:2005svg}.
        \item Gluon-gluon: $H \rightarrow gg$ + (partons),
        the decay of a Higgs boson into a pair of gluons with QCD from the gluon pair \cite{Gehrmann-DeRidder:2005alt}.
    \end{itemize}
    Along with the tree-level antenna, there are also the
    one-loop antennae. For the three-parton case these are given by
    \begin{equation}\label{eqn:X31}
        X_{3}^{1}(i,j,k) = S_{ijk,IK} \dfrac{|M_{n+1}^{(1)}(i,j,k)|^{2}}{|M_{n}^{(0)}(I,K)|^{2}} - X_{3}^{0}(i,j,k) \dfrac{|M_{n}^{(1)}(I,K)|^{2}}{|M_{n}^{(0)}(I,K)|^{2}} \, ,
    \end{equation}
    where $X_{3}^{1}$ are defined such that they are proportional
    to the one-loop singular functions. Since the one-loop
    factorisation formulae (\ref{eqn:1L_soft_factorisation})
    and (\ref{eqn:1L_collinear_factorisation}) are of the form
    $|M^{(1)}_{n+1}|^{2}\rightarrow S^{(0)}|M^{(1)}_{n}|^{2} + S^{(1)}|M^{(0)}_{n}|^{2}$,
    the term proportional to $X_{3}^{0}$ has to be removed
    to fulfill this requirement.
    The antenna functions are summarised in Table~\ref{table:antenna_functions}, where
    antenna functions are categorised by their class and radiative
    processes. A pictorial representation is also given in Figure~\ref{fig:antenna}.

@@

    Below we list the antenna functions relevant
    for multijet production in electron-positron
    annihiliation with a single quark flavour,
    namely the partonic channel $e^{-}e^{+} \rightarrow
    d \bar{d}$ + $ng$.
    For this we require the $A$, $D$, and $F$ antenna functions,
    see Table~\ref{table:antenna_functions}.
    The $i,j,k$ indices will be fixed such that $d = 1$, $\bar{d} = 2$,
    and $g \in \{3, 4, 5\}$.

    It will be useful to define the $\mathcal{P}oles$
    and $\mathcal{F}inite$ operators to extract the
    singular and finite contributions from an antenna
    function. However, there are still finite terms
    from the $\mathcal{P}oles$ operator coming from
    the IR singularity operators (cite here). Therefore,
    care has to be taken to extract all the finite
    remainders from the antenna functions.

    For the one-loop antenna functions, there are three
    different functions corresponding to the: leading colour,
    subleading colour, and closed quark look contributions.
    It is sufficient to consider the leading colour
    structure in this thesis as the remaining contributions
    are subleading. They become important when
    building subtraction terms to exactly cancel divergences
    but we do not require this level of accuracy for
    our applications.

    \subsection{Quark-antiquark antenna functions}
    The quark-antiquark antenna functions are derived by normalising
    the colour-ordered QCD radiative corrections to $\gamma^{*} \rightarrow q \bar{q}$
    at NNLO.

    \subsubsection{Three-parton tree-level antenna function}
    The tree-level three-parton antenna function is given by
    \begin{equation}\label{eqn:A30}
        A_{3}^{0}(1_{q}, 3_{g}, 2_{\bar{q}}) = \dfrac{1}{s_{123}}\left(\dfrac{s_{13}}{s_{23}} + \dfrac{s_{23}}{s_{13}} + 2\dfrac{s_{12}s_{123}}{s_{13}s_{23}}\right) + \mathcal{O}(\epsilon)
    \end{equation}
    where the IR structure is apparent. The first two terms
    correspond to the gluon going collinear with the quark
    and antiquark, where as the final term accounts for the soft
    limit.

    \subsubsection{Three-parton one-loop antenna function}
    The leading colour one-loop antenna functions are
    given by
    \begin{align}\label{eqn:A31}
        \mathcal{P}oles\left(A_{3}^{1}(1_{q}, 3_{g}, 2_{\bar{q}})\right) =& \; 2\left(\mathbf{I}_{qg}^{(1)}(\epsilon, s_{13}) + \mathbf{I}_{qg}^{(1)}(\epsilon, s_{23}) - \mathbf{I}_{q\bar{q}}^{(1)}(\epsilon,s_{123})\right)A_{3}^{0}(1_{q},3_{g},2_{\bar{q}}) \, , \\
        \mathcal{F}inite\left(A_{3}^{1}(1_{q}, 3_{g}, 2_{\bar{q}})\right) =& -\left(R(y_{13}, y_{23}) + \dfrac{5}{3}\log{y_{13}}+\dfrac{5}{3}\log{y_{23}}\right)A_{3}^{0}(1_{q}, 3_{g}, 2_{\bar{q}}) \nonumber\\
        &+\dfrac{1}{s_{123}} + \dfrac{s_{12}+s_{23}}{2s_{123}s_{13}} + \dfrac{s_{12}+s_{13}}{2s_{123}s_{23}} \nonumber \\
        &-\dfrac{s_{13}}{2s_{123}(s_{12}+s_{13})}-\dfrac{s_{23}}{2s_{123}(s_{12}+s_{23})} \nonumber \\
        &+\dfrac{\log{y_{13}}}{s_{123}}\left(2-\dfrac{1}{2}\dfrac{s_{13}s_{23}}{(s_{12}+s_{23})^{2}} + 2\dfrac{s_{13}-s_{23}}{s_{12}+s_{23}}\right) \nonumber  \\
        &+\dfrac{\log{y_{23}}}{s_{123}}\left(2-\dfrac{1}{2}\dfrac{s_{13}s_{23}}{(s_{12}+s_{13})^{2}} + 2\dfrac{s_{23}-s_{13}}{s_{12}+s_{13}}\right) \, , 
    \end{align}
